Gut-resident microbial species and their genes are associated with cognition and neuroanatomy in children

### 2023-03-29 manuscript/main.tex
updates to acknowledgements

All data needed to evaluate the conclusions in the paper
are present in the paper and/or the Supplementary Materials.
Taxonomic and functional microbial profiles, as well as subject
demographics necessary for statistical analyses and machine learning are
available on the Open Science Framework
\cite{bonhamECHORESONANCEMicrobiome2022}.
Data processing, generation of summary statistics, and
generation of plots was performed using the julia programming language
\cite{bezansonJuliaFreshApproach2017,
    bonhamMicrobiomeJlBiobakeryUtils2021,
    danischMakieJlFlexible2021,
    blaomMLJJuliaPackage2020,
    ben_sadeghi_2022_7359268,
    dahua_lin_2023_7695673,
    douglas_bates_2023_7734970,
    douglas_bates_2023_7734970,
    kevin_bonham_2023_7647510}.
All code for data analysis and figure generation, as well as scripts for automated
download of input files are available on github \cite{kevin_bonham_2023_7647510}.

@@

KSB, VKC, CH, and SD were responsible for conceptualization,
methodology and project administration.
VKC, SD, and VD were responsible for funding aqusition.
KSB, MB, FB, RCL, and JB contributed to data curation.
Formal analyses were conducted by KSB, GFB, and MB.
Investigation was performed by KSB, GFB, SHM, EW, FB, RCL, and MB.
Resources were provided by SHM, EW, FB, RCL, JB, CH, and MB.
Software and data visualizations were produced by KSB and GFB.
KSB, MB, SD, VD, and VKC were responsible for supervision.
Validation was performed by KSB, SHM, JB, and MB.
KSB and GFB wrote the initial draft, 
and review and editing were provided by SD, CH, and VKC.

>>>>

All data needed to evaluate the conclusions in the paper
are present in the paper and/or the Supplementary Materials.
Taxonomic and functional microbial profiles, as well as subject
demographics necessary for statistical analyses and machine learning are
available on the Open Science Framework
\cite{bonhamECHORESONANCEMicrobiome2022}.
Data processing, generation of summary statistics, and
generation of plots was performed using the julia programming language
and 3rd party packages
\cite{bezansonJuliaFreshApproach2017,
    bonhamMicrobiomeJlBiobakeryUtils2021,
    danischMakieJlFlexible2021,
    blaomMLJJuliaPackage2020,
    ben_sadeghi_2022_7359268,
    dahua_lin_2023_7695673,
    douglas_bates_2023_7734970}.
Information for replicating the package environment
as well as code for data analysis and figure generation, as well as scripts for automated
download of input files are available on github \cite{kevin_bonham_2023_7647510}.

@@

KSB, VKC, CH, and SD were responsible for conceptualization,
methodology and project administration.
VKC, SD, and VD were responsible for funding aqusition.
KSB, SHM, MB, FB, RCL, and JB contributed to data curation.
Formal analyses were conducted by KSB, GFB, and MB.
Investigation was performed by KSB, GFB, SHM, EW, FB, RCL, and MB.
Resources were provided by SHM, EW, FB, RCL, JB, CH, and MB.
Software and data visualizations were produced by KSB and GFB.
KSB, MB, SD, VD, and VKC were responsible for supervision.
Validation was performed by KSB, SHM, JB, and MB.
KSB and GFB wrote the initial draft, 
and review and editing were provided by SD, CH, and VKC.
